Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-12 main.Rmd
add normal and gamma

This section desctibes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.

@@

Observations from the null distribution are chosen as:  
`sim_norm_null =   distributional::dist_normal(5, 10)`  
`sim_exp_null  =   distributional::dist_expoential(5)`  
`sim_gamma_null  =   distributional::dist_gamma(0.5, 2)`  
`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`

@@

```{r}
# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
# all_files
# 
# read_files = lapply(all_files, function(x){
#   read_rds(paste0("../hakear-drake/data/", x))
# })
# 
# names(read_files) = str_remove(all_files, pattern = ".rds")
# 
# null_all = bind_rows(normal = read_files$null_normal,
#                      exponential = read_files$null_exp,
#                      gamma = read_files$null_gamma,
#                      weibull = read_files$null_weibull,
#                      .id = "distribution")
design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
design_all$design = 
  factor(design_all$design,
         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
design_all$distribution = 
  factor(design_all$distribution,
         levels = c("normal","exponential", "gamma", "weibull"), labels = c("norm", "exp", "gam", "wei"))
library(dplyr)
library(ggplot2)
ggplot2::ggplot(design_all %>% 
                      filter(design == "D1")) +
  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
  facet_grid(nx~nfacet) +
  scale_fill_viridis_d() +
  xlab("MMPD")
```

>>>>

This section describes the design of simulation runs, in terms of the scenarios simulated, the number of permutations used to compute estimates and to display the distribution of MMPD.

@@

Observations from the null distribution are chosen as:  
`sim_norm_null =   distributional::dist_normal(5, 10)`  
<!--`sim_exp_null  =   distributional::dist_expoential(5)`  -->
`sim_gamma_null  =   distributional::dist_gamma(0.5, 0.2)`  
<!--`sim_weibull_null  =   distributional::dist_weibull(1.5, 3)`-->

@@

Currently, we see that the normalisation works fine for each facet since the distributions for each column are equal irrespective of the distribution type. But it does not work along the x-axis.

```{r}
# all_files = list.files(path = "../hakear-drake/data", pattern = ".rds")
# all_files
# 
# read_files = lapply(all_files, function(x){
#   read_rds(paste0("../hakear-drake/data/", x))
# })
# 
# names(read_files) = str_remove(all_files, pattern = ".rds")
# 
# null_all = bind_rows(normal = read_files$null_normal,
#                      exponential = read_files$null_exp,
#                      gamma = read_files$null_gamma,
#                      weibull = read_files$null_weibull,
#                      .id = "distribution")
# design_all = readr::read_rds("../hakear-drake/data/design_all.rds")
design_all = readr::read_rds("data/design_all.rds")

design_all$design = 
  factor(design_all$design,
         levels = c("null","vary_f", "vary_x", "vary_all"), labels = c("D1", "D2", "D3", "D4"))
design_all$distribution = 
  factor(design_all$distribution,
         levels = c("normal","gamma"), labels = c("norm","gam"))
library(dplyr)
library(ggplot2)
ggplot2::ggplot(design_all %>% 
                      filter(design == "D1")) +
  ggridges::geom_density_ridges(aes(y = distribution, x = mmpd.x, fill = distribution)) + 
  facet_grid(nx~nfacet) +
  scale_fill_viridis_d() +
  xlab("MMPD")
```
